\documentclass[ENG,PhD]{official/lti-tech-report}
%\documentclass[ENG,MSc,DRAFT]{cinvestav}

%%%%%%%%% PACKAGES
\usepackage{color}
%\usepackage{algorithmic}
\usepackage{latexsym, amssymb}
\usepackage{xcolor}
\usepackage{pstricks}
\usepackage{epsfig}
\usepackage{ucs}
\usepackage{lettrine}
\usepackage[utf8x]{inputenc}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{url}
\usepackage{pseudocode}
\usepackage{longtable}

\RequirePackage{hyperref}
\RequirePackage{algorithm}
\usepackage{algorithmic}
\usepackage{latexsym, amssymb}
%\usepackage{subfigure}
\usepackage{fancybox}
\usepackage{rotating}
\usepackage{pdflscape} 
\usepackage{multirow}
\usepackage{textcomp}
\usepackage{tabularx,ragged2e}
\usepackage{booktabs}
\usepackage{subcaption}

\newcommand{\V}[1]{\mathbf{#1}}

\graphicspath{ {./images/} }

\title{Smart Usage of Context Information for the Analysis, Design, and Generation of Power-Aware Policies for Mobile Sensing Apps}
\shorttitle{Smart Usage of Context Information for the Generation of Power-Aware Policies}
\author{Rafael Pérez Torres, César Torres Huitzil and Hiram Galeana Zapién}
\adscripcion{Cinvestav Tamaulipas. Parque Cient\'ifico y Tecnol\'ogico TecnoTam -- Km. 5.5 Carretera Cd. Victoria-Soto La Marina. C.P. 87130 Cd. Victoria, Tamps. }
\city {Cd. Victoria, Tamaulipas, Mexico.}
%\date{December, 2010}
\techreportnumber{07}
\publishedmonth{December} %mes de la publicación
\publishedday{5th} %día de la publicación
\publishedyear{2014} %año de la publicación
\keywords{wii1, wii2, wii3}
\correspondingauthor{Rafael Pérez Torres $<$rperez@tamps.cinvestav.mx$>$, César Torres Huitzil $<$ctorres@tamps.cinvestav.mx$>$ and Hiram Galeana Zapién $<$hgaleana@tamps.cinvestav.mx$>$}
\grants{}
\dateofsubmission{December 5th, 2014}
\tobecited{Rafael Pérez Torres, César Torres Huitzil, Hiram Galeana Zapién. Smart Usage of Context Information for the Analysis, Design, and Generation of Power-Aware Policies for Mobile Sensing Apps. CINVESTAV Tamaulipas. 2014 Nov. 80000 pp. Technical Report No. LTI-TR-2014-07}
\placeanddateofpublication{Ciudad Victoria, Tamaulipas, MEXICO.}

\include{sections/abstract}

\begin{document}
\makeintropages
\include{sections/preamble}
\include{sections/theoretical-framework}
\include{sections/state-of-art}
\bibliographystyle{siam}
\bibliography{../../../resources/references/bibliography}
\end {document}
